\documentclass[a4paper,12pt]{article}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{enumerate}
\usepackage{fancyhdr}
\usepackage{geometry}

% Set page margins
\geometry{top=1in, bottom=1in, left=1in, right=1in}

% Header and Footer configuration
\pagestyle{fancy}
\fancyhead[L]{MCA Examination}
\fancyhead[C]{Semester - I}
\fancyhead[R]{Time: 3 Hours}
\fancyfoot[C]{Page \thepage}

% Title configuration
\title{MCA Examination\\
       Semester - I\\
       Subject: Computer Science Fundamentals\\
       Maximum Marks: 50}
\author{}
\date{}

\begin{document}

\maketitle

\section*{Section A: Multiple Choice Questions (15 Marks)}

\begin{enumerate}
    \item Which of the following is the main function of the CPU?
    \begin{enumerate}
        \item Store data
        \item Execute instructions
        \item Provide output
        \item None of the above
    \end{enumerate}
    (5 Marks)

    \item Which of the following is a high-level programming language?
    \begin{enumerate}
        \item Assembly Language
        \item C++
        \item Machine Language
        \item Binary Code
    \end{enumerate}
    (5 Marks)

    \item In which year was the first computer virus discovered?
    \begin{enumerate}
        \item 1970
        \item 1983
        \item 1986
        \item 1990
    \end{enumerate}
    (5 Marks)

   

\newpage 

\section*{Section B: Short Answer Questions (35 Marks)}

\begin{enumerate}
    \item Explain the concept of a "Stack" in data structures with an example. (5 Marks)\\
    
    \item What is the difference between primary key and foreign key in relational databases? (5 Marks)\\
    
    \item Define the term "Object-Oriented Programming". List the four main principles of OOP. (5 Marks)\\
    
    \item Write a C++ program to find the factorial of a number using recursion. (5 Marks)\\
    
    \item What is the difference between a process and a thread? (5 Marks)\\
    
    \item Explain the different types of software licenses. (5 Marks)\\
    
    \item Describe the concept of a "Linked List" and its advantages over arrays. (5 Marks)\\
\end{enumerate}
\end{document}